\documentclass{article}

% Packages required to support encoding
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx} 
% Packages required by code

% Packages always used
\usepackage{listings}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage[usenames,dvipsnames]{color}
\hypersetup{colorlinks=true,urlcolor=blue}


\usepackage[framed,numbered,autolinebreaks,useliterate] {mcode}

\input{homework.tex}


\begin{document} 



\hypertarget{problem_0_homework_checklist_2}{}
\subsection*{{Problem 0: Homework checklist}}
\label{problem_0_homework_checklist_2}

\checkmark	I didn't talk with any one about this homework. \newline
\checkmark 	Source-code are included at the end of this document. 


\hypertarget{problem_1_prove_or_disprove_3}{}
\subsection*{{Problem 1: Prove or disprove}}
\label{problem_1_prove_or_disprove_3}

For the proof below, I will assume all the matrices are $n\times n$ square matrices.                                                                

\begin{enumerate}%        

\item The product of two diagonal matrices is diagonal. \newline
$\mA $  and  $\mB $ are diagonal matrices, so \newline 
$\mA_{ij}= 0, if \ i\neq j $  \newline
$\mB_{ij}= 0, if \ i\neq j $  \newline
$\mC = \mA\times\mB$ \newline
$\mC_{ij}=\sum_{k=1}^{n}{\mA_{ik}\mB_{kj}} $\newline
Only if $i=j=k$, $\mC_{ij} $ will not be zero, which mean $\mC$ is also a diagonal matrix. 

\item The product of two upper triangular matrices is upper triangular
$\mA $  and  $\mB $ are two upper triangular matrices, so \newline 

$\mA_{ij}= 0, if  \ i \geqslant j $  \newline
$\mB_{ij}= 0, if \ i\geqslant j $  \newline
$\mC = \mA\times\mB$ \newline
$\mC_{ij}=\sum_{k=1}^{n}{\mA_{ik}\mB_{kj}} $\newline
When $i\geqslant j $, $\mC_{ij}=0 $ because one of $\mA_{ik} $ and $\mB_{kj} $ must be zero. 



\item The product of two symmetric matrices is symmetric.
$\mA $  and  $\mB $ are two symmetric matrices, so \newline 

$\mA_{ij}= \mA_{ji} , if \  i = j $  \newline
$\mB_{ij}= \mB_{ji} , if\  i = j $  \newline
$\mC = \mA\times\mB$ \newline
$\mC_{ij}=\sum_{k=1}^{n}{\mA_{ik}\mB_{kj}} $\newline
Then $\mC_{ij} $ is not necessary to be equal to $\mC_{ji} $\newline
Counter-example: \newline
$\mA=\bmat{1&1\\1&2}$ is a symmetric matrix; \newline
$\mB=\bmat{1&1\\1&1}$ is also a symmetric matrix.\newline
$\mC = \mA\times\mB = \bmat{2&2\\3&3} $ which is not a symmetric matrices.  \newline


\item The product of two orthogonal matrices is orthogonal.

\item The product of two square, full rank matrices is full rank
This statement is incorrect. \\
Counter-example:
$\mA=\bmat{1&1\\1&2}$ is a full rank matrix; \newline
$\mB=\bmat{3&5\\1&1}$ is also a full rank matrix.\newline
$\mC = \mA\times\mB = \bmat{4&6\\2&3} $ which is not a full matrices.  \newline



\end{enumerate}

\end{document}



















